Overview

### 2021-05-11 overview_gh.Rmd
using cli to make nicer interface

```{r step1}
oolong_test_rater1 <- create_oolong(abstracts_stm, abstracts$text)
```

@@

```{r step2}
oolong_test_rater2 <- clone_oolong(oolong_test_rater1)
```

@@

```{r, eval = FALSE}
## Let rater 1 do the test.
oolong_test_rater1$do_word_intrusion_test()
oolong_test_rater1$do_topic_intrusion_test()
oolong_test_rater1$lock()

## Let rater 2 do the test.
oolong_test_rater2$do_word_intrusion_test()
oolong_test_rater2$do_topic_intrusion_test()
oolong_test_rater2$lock()
```

@@

```{r}
trump <- create_oolong(input_corpus = trump2k, exact_n = 40)
trump2 <- clone_oolong(trump)
```

>>>>

```{r step1}
oolong_test_rater1 <- create_oolong(abstracts_stm, abstracts$text, userid = "joe")
```

@@

```{r step2}
oolong_test_rater2 <- clone_oolong(oolong_test_rater1, userid = "donald")
```

@@

```{r, eval = FALSE}
## Let donald do the test.
oolong_test_rater1$do_word_intrusion_test()
oolong_test_rater1$do_topic_intrusion_test()
oolong_test_rater1$lock()

## Let joe do the test.
oolong_test_rater2$do_word_intrusion_test()
oolong_test_rater2$do_topic_intrusion_test()
oolong_test_rater2$lock()
```

@@

```{r}
trump <- create_oolong(input_corpus = trump2k, exact_n = 40, userid = "joe")
trump2 <- clone_oolong(trump, userid = "donald")
```
